### 2015-01-27 src/paper4/p4_discussion.tex
Updated papers

As it becomes impossible to distinguish between body- and world-fixed fixation point at far fixation distances, the lack of scaling could - in theory - be explained by participants incorrectly perceiving both the body- and world-fixed far fixation points as being body-fixed. This is unlikely because the target displacement associated with a world-fixed target was between X and Y degrees in our experiment, which is easily perceivable especially given that the target was foveated. This adds confidence to our hypothesis that eye movements indeed influence self-motion perception, with moderate to no scaling for fixation depth.

% Relation to Clemens, 2015
\begin{figure}
    \includegraphics[width=0.5\textwidth]{src/paper4/paper4_figure6.eps}

    \caption{...}
    \label{p4:fig6}
\end{figure}

@@

[Conclusion]

>>>>

% FIXME: Change X and Y in paragraph below
As it becomes impossible to distinguish between body- and world-fixed fixation point at far fixation distances, the lack of scaling could - in theory - be explained by participants incorrectly perceiving both the body- and world-fixed far fixation points as being body-fixed. This is unlikely because the target displacement associated with a world-fixed target was between X and Y degrees in our experiment, which is easily perceivable especially given that the target was foveated. This adds confidence to our hypothesis that eye movements indeed influence self-motion perception, with moderate to no scaling for fixation depth.

% Relation to Clemens, 2015
\begin{wrapfigure}{l}[5pt]{0.5\textwidth}
    \includegraphics[width=1.0\textwidth]{src/paper4/p4_figure6.pdf}

    \caption{...}
    \label{p4:fig6}
\end{wrapfigure}

@@

% Conclusion
In summary, fixation depth is not properly taken into account, suggesting that a relatively raw eye movement signal is used in self-motion perception. While efference copies of the eye movement signals or proprioceptive feedback could be directly responsible for the perceived self-motion, it cannot be ruled out that the signals that drive the eye movements, especially those caused by the LVOR, are not causing the reported effect instead.
